\documentclass{resume}
\usepackage[left=0.2 in,top=0.25in,right=0.2 in,bottom=0.25in]{geometry}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Arkapravo Ghosh}
\address{+91 89101 48428 \\ Kolkata, West Bengal, India}
\address{\href{mailto:arkapravoghosh99@gmail.com}{arkapravoghosh99@gmail.com} \\ \href{https://www.linkedin.com/in/arkapravo-ghosh}{www.linkedin.com/in/arkapravo-ghosh} \\ \href{https://github.com/Arkapravo-Ghosh}{github.com/Arkapravo-Ghosh}}
\begin{document}
\vspace{-0.4em}
\begin{rSection}{EXPERIENCE}
	{\bf Junior Software Engineer} \hfill {Aug 2025 -- Present}\\
	Goodfit \hfill {Full-time, Remote}
	\vspace{-0.4em}
	\begin{itemize}
		\item{Architect, develop, and maintain the Goodfit platform, delivering high-performance features and optimizing existing functionalities for scalability and reliability.}
		\item{Collaborate with cross-functional teams including designers, product managers, and QA engineers to implement responsive, user-friendly interfaces aligned with UX best practices.}
		\item{Produce clean, maintainable, and well-documented code; perform peer code reviews to enforce coding standards and reduce defects.}
		\item{Leverage React.js, Next.js, TypeScript, Tailwind CSS, PostgreSQL, and REST API integration to build reusable front-end and back-end components.}
		\item{Apply Kanban methodology to manage continuous delivery workflows, track tasks efficiently, and ensure rapid, high-quality releases.}
	\end{itemize}
	{\bf Software Development Engineer} \hfill {May 2025 -- Aug 2025}\\
	PredictGrowth \hfill {Full-time, Remote}
	\vspace{-0.4em}
	\begin{itemize}
		\item{Engineered and enhanced the PredictGrowth AI Platform, implementing REST APIs and optimizing database queries to improve platform responsiveness by 10\%.}
		\item{Introduced efficient state management in the front-end, reducing load time by 20\% and improving user experience.}
		\item{Collaborated in Agile sprints, ensuring timely delivery of features while maintaining high code quality through automated testing and code reviews.}
		\item{Integrated cloud infrastructure services on AWS to improve system scalability and fault tolerance.}
	\end{itemize}
	{\bf Software Development Engineer} \hfill {Feb 2024 -- May 2025}\\
	RevMaxx \hfill {Part-time, Hybrid}
	\vspace{-0.4em}
	\begin{itemize}
		\item{Designed, built, and maintained the backend architecture for the RevMaxx AI Platform, enabling rapid onboarding of enterprise clients.}
		\item{Improved platform performance by 30\% through database query optimization and implemented WebSocket-based real-time data transfer, increasing responsiveness by 20\%.}
		\item{Applied security best practices by enforcing authentication, access control, and dependency management, resulting in zero critical vulnerabilities.}
		\item{Utilized Docker for containerization and Git-based CI/CD pipelines for continuous integration and deployment.}
	\end{itemize}
	{\bf Software Development Engineer} \hfill {Sep 2024 -- Nov 2024}\\
	Rad Media Solutions \hfill {Part-time, Remote}
	\vspace{-0.4em}
	\begin{itemize}
		\item{Developed custom enterprise-grade software solutions using Angular, RESTful APIs, and cloud-based deployment strategies.}
		\item{Conducted requirement gathering sessions with clients to ensure delivered solutions met business needs and technical specifications.}
		\item{Optimized applications for cross-browser compatibility and responsive design to ensure seamless multi-device usage.}
	\end{itemize}
	{\bf Software Development Engineer} \hfill {Jul 2024 -- Aug 2024}\\
	Avinya NeuroTech \hfill {Part-time, Remote}
	\vspace{-0.4em}
	\begin{itemize}
		\item{Developed and maintained the frontend for Avinya NeuroTech’s AI-driven healthcare analytics platform, improving accessibility and reducing the onboarding time for new users.}
		\item{Implemented responsive design principles, optimized performance for cross-device compatibility, and integrated REST APIs with WebSocket technology to deliver secure, real-time data insights.}
	\end{itemize}
	{\bf Software Development Engineer} \hfill {Apr 2024 -- May 2024}\\
	Connect AI \hfill {Freelance, Remote}
	\vspace{-0.4em}
	\begin{itemize}
		\item{Implemented front-end features and reusable UI components for the Connect AI Platform, ensuring alignment with UX/UI design guidelines.}
		\item{Collaborated with backend developers to integrate RESTful APIs, improving feature delivery speed.}
	\end{itemize}
	{\bf Software Development Engineer} \hfill {Jun 2023 -- Dec 2023}\\
	PepHub \hfill {Part-time, Remote}
	\vspace{-0.4em}
	\begin{itemize}
		\item{Configured and deployed applications on AWS and DigitalOcean, increasing scalability by 40\% and improving uptime.}
		\item{Built secure CI/CD pipelines using Git and Docker, reducing deployment time by 30\% and eliminating downtime during releases.}
		\item{Developed the \href{https://consultancy.pephub.tech}{PepHub Consultancy Website}, increasing lead generation and client acquisition.}
		\item{Maintained the company’s software infrastructure and internal tools to ensure continuous availability and performance.}
	\end{itemize}
\end{rSection}
\vspace{-0.4em}
\begin{rSection}{SKILLS}
	\begin{itemize}
		\item \textbf{Programming Languages:} JavaScript, TypeScript, Python, Bash/Shell Scripting
		\item \textbf{Frontend Development:} React.js, Next.js, Angular, React Native, SCSS, Tailwind CSS, Responsive Web Design, UI/UX Design (Figma)
		\item \textbf{Backend Development:} Node.js, Express.js, FastAPI, RESTful APIs, WebSocket Integration
		\item \textbf{Databases:} MySQL, MariaDB, PostgreSQL, MongoDB
		\item \textbf{DevOps \& CI/CD:} Linux (GNU/Linux), Git, GitHub, Docker, Docker Compose, Networking, Jenkins, Kubernetes, CI/CD Pipeline Automation
		\item \textbf{Cloud Platforms:} Google Cloud Platform (GCP), Amazon Web Services (AWS), Microsoft Azure, DigitalOcean
		\item \textbf{IoT \& Embedded Systems:} Arduino, Raspberry Pi, Node-RED
	\end{itemize}
\end{rSection}
\vspace{-0.4em}
\begin{rSection}{Education}
	\textbf{Bachelor of Technology in Computer Science and Engineering}\hfill {Expected 2026}\\
	\textbf{(IoT, Cybersecurity and Blockchain Technology)}\\
	University of Engineering and Management, Kolkata \hfill  7.44 GPA
\end{rSection}
\vspace{-0.4em}
\begin{rSection}{PROJECTS}
	\begin{itemize}
		\item \textbf{\href{https://github.com/Arkapravo-Ghosh/speech-to-text}{Speech To Text API:}} Developed an open-source RESTful API for speech-to-text conversion using Python, FastAPI, and OpenAI's Whisper v3 model via HuggingFace Transformers. Implemented audio preprocessing, asynchronous processing, and JSON-based responses for scalable integration.

		\item \textbf{\href{https://github.com/Arkapravo-Ghosh/Smart-Parking-System}{Smart Parking System:}} Engineered an IoT-based parking management solution using Raspberry Pi, Node.js, Express.js, and React.js. Designed a real-time slot availability tracker using WebSockets and integrated with a responsive web dashboard for live monitoring.

		\item \textbf{\href{https://github.com/Arkapravo-Ghosh/attendance-monitoring-system}{Biometric Attendance Management System:}} Built an IoT-powered attendance tracking system with fingerprint authentication using Python, MariaDB, Raspberry Pi, and a biometric fingerprint sensor. Designed an admin console for record management and automated data synchronization.

		\item \textbf{\href{https://github.com/Arkapravo-Ghosh/icd10-scrapper}{ICD-10 Medical Coding Scraper:}} Created a web scraping utility in TypeScript with Node.js and Cheerio to extract and update ICD-10 medical codes from \href{https://www.icd10data.com}{icd10data.com}, storing results in structured JSON format for healthcare application integration.
	\end{itemize}
\end{rSection}
\vspace{-0.4em}
\end{document}
